The use of Synchronous and asynchronous e-learning methods efficiency comparison\thanks{Semestrálny projekt v predmete Metódy inžinierskej práce, ak. rok 2015/16, vedenie: Ing. Jozef Sitarčík}

### 2020-10-30 Article.tex
(worked on introduction

\pagestyle{headings}

\title{The use of Synchronous and asynchronous e-learning methods and the comparison between them.\thanks{Semestrálny projekt v predmete Metódy inžinierskej práce, ak. rok 2015/16, vedenie: Meno Priezvisko}} % meno a priezvisko vyučujúceho na cvičeniach

@@

\begin{abstract}
\ldots
\end{abstract}

\section{Abstract}

Sychronous learning happens in real-time with instantenous interaction between the participants.(Chat,Face-to-Face videocall  etc..)~\ref{nejaka}.
On the other hand Asynchronous e-learning 
is self-paced and allows individuals to gain or exchange information with each-other but not instantaneously.(e-mail
blogs, forums,websites etc..)~\ref{nejaka}.
People have been trying to prove one method's superiority over the other in order to use the better method for teaching.
Although in reality neither one is better than the other. Both methods should be used in e-learning , however
in different ways  and  in different scenarios. In this article I will talk about where and when to use asynchronous and
synchronous e-learning methods.~\ref{nejaka}. It is based on a small study done by Stefan Hrastinski.~\ref{nejaka}.
The goal of this article is to show the pros and cons of the two learning methods, and how to use them.
~\ref{nejaka}.
Dôležité súvislosti sú uvedené v častiach~\ref{dolezita} a~\ref{dolezitejsia}.
Záverečné poznámky prináša časť~\ref{zaver}.

\section{Nejaká časť} \label{nejaka}

@@

\begin{figure*}[tbh]
\centering
%\includegraphics[scale=1.0]{diagram.pdf}
Aj text môže byť prezentovaný ako obrázok. Stane sa z neho označný plávajúci objekt. Po vytvorení diagramu zrušte znak \texttt{\%} pred príkazom \verb|\includegraphics| označte tento riadok ako komentár (tiež pomocou znaku \texttt{\%}).
\caption{Rozhodujúci argument.}
\label{f:rozhod}
\end{figure*}

\section{Iná časť} \label{ina}

Základným problémom je teda\ldots{} Najprv sa pozrieme na nejaké vysvetlenie (časť~\ref{ina:nejake}), a potom na ešte nejaké (časť~\ref{ina:nejake}).\footnote{Niekedy môžete potrebovať aj poznámku pod čiarou.}

@@

Niekedy treba uviesť zoznam:

\begin{itemize}
\item jedna vec
\item druhá vec
	\begin{itemize}
	\item x
	\item y
	\end{itemize}
\end{itemize}

@@

\subsection{Ešte nejaké vysvetlenie} \label{ina:este}

@@

\section{Dôležitá časť} \label{dolezita}

\section{Ešte dôležitejšia časť} \label{dolezitejsia}

\section{Záver} \label{zaver} % prípadne iný variant názvu

>>>>

\pagestyle{plain}

\title{The use of Synchronous and asynchronous e-learning methods efficiency comparison\thanks{Semestrálny projekt v predmete Metódy inžinierskej práce, ak. rok 2015/16, vedenie: 	
Ing. Jozef Sitarčík}} % meno a priezvisko vyučujúceho na cvičeniach

@@

\begin{abstract}
\ldots
People have been trying to prove one method's superiority over the other in order to use the better method for teaching.
Although in reality neither one is better than the other. Both methods should be used in e-learning , however
in different ways  and in different scenarios. The main purpose of this article is to discuss  where and when to use asynchronous and
synchronous e-learning methods to achieve efficient e-learning. It is based mainly on two studies, Stefan Hrastinski's study of "Asynchronous and Synchronous E-Learning"~\ref{source1}, and the other is Ayesha Perveen's study: "Synchronous and Asynchronous E-Language Learning:A Case Study of Virtual University of Pakistan"~\ref{source2}
The goal of this article is to show the pros and cons of the two learning methods, and when and how to use them.
\end{abstract}

\section{Introduction} \label{intro}

Online learning environments have become widespread phenomenon in 21st century, but their efficiency has been a controversial topic between scientist for decades. Especially in the early days of Online e-learning, where online telecommunication application such as Skype,Discord,Google Meet etc... were not widespread nor available for an average person for either technical or financial reasons,  that meant real-time face-to-face communication was not possible, which made e-learning less desirable, since Synchronous learning was not available yet. However in the modern days, we have a great amount of online telecommunication applications and improvements in technology and increasing bandwidth capabilities have led to the growing popularity of e-learning, therefore both Asynchronous and Synchronous e-learning is possible nowadays.
Synchronous learning happens in real-time with immediate interaction between the participants, which has been considered by many as the superior e-learning method, for a while because of the social aspect of learning, even though studies suggest that is not entirely accurate.
On the other hand, Asynchronous e-learning is self-paced and not time bound, which means that the individual can learn whenever he wants or feels like it.This has been around for time in a form of Distance education or distance learning.The article is based on one small scale scale study by Stefan Hrastinski and one large scale case study done by Ayesha Perveen , who based study on the Virtual University of Pakistan. The article will also explain the Synchronous e-learning method~\ref{sync}.
Asynchronous e-learning method~\ref{async}, Benefits and Disadvantages of both methods,~\ref{badose}~\ref{badoae}
and the most efficient way to use them together to achieve high level e-learning~\ref{comb}. 
Finally, in the conclusion ads dw will be discussed~\ref{conc}

\footnote{Distance education : also called distance learning is the education of students who may not always be physically present at school, through mail or other methods.}

\section{Synchronous E-learning} \label{sync}

@@

\begin{figure*}[tbh]
\begin{center}
    \includegraphics[scale=1.0]{diagram.pdf}
%Aj text môže byť prezentovaný ako obrázok. Stane sa z neho označný plávajúci objekt. Po vytvorení diagramu zrušte znak \texttt{\%} pred príkazom \verb|\includegraphics| označte tento riadok ako komentár (tiež pomocou znaku \texttt{\%}).
\caption{Rozhodujúci argument.}
\label{f:rozhod}
\end{center}

List of applications for synchronous e-learning:
\begin{itemize}
\item jedna vec
\item druhá vec
	\begin{itemize}
	\item x
	\item y
	\end{itemize}
\end{itemize}

\end{figure*}

\section{Asynchronous E-learning} \label{async}

Základným problémom je teda\ldots{} Najprv sa pozrieme na nejaké vysvetlenie (časť~\ref{ina:nejake}), a potom na ešte nejaké (časť~\ref{ina:nejake}).

@@

@@

\subsection{Types of commu} \label{ina:este}

@@

\section{Benefits and disadvantages of synchronous E-learning} \label{badose}

\section{Benefits and disadvantages of Asynchronous E-learning} \label{badoae}

\section{Efficiency of the Combination of Asynchronous and Synchronous E-learning } \label{comb}

\section{Conclusion} \label{conc} % prípadne iný variant názvu
